Generalized Bradley-Terry models

### 2025-02-20 inst/jss_hyper3_real.Rnw
instructions how to process
consistentification

@@

<<readsushi>>=
a <- as.matrix(read.table("sushi.txt"))
head(a)
@

@@

<<tryH,cache=TRUE>>=
wanted <- sample(seq_len(nrow(a)), 50, replace=TRUE, prob=a[,1])
H1888 <- make_sushi_H(a[wanted,-1], strength=1.888)
H1000 <- make_sushi_H(a[wanted,-1], strength=1.000)
@

<<calclikesushi, cache=TRUE>>=
f <- function(strength){
   H <- make_sushi_H(a[wanted,-1], strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=4,len=5)
L <- sapply(s,f)
@

@@

<<justf1>>=
f1 <- f(1)
@

<<diffmaxlike>>=
f1 - max(L)
@

>>>>

%  Process with:
%  
%  Rscript -e 'library("knitr") ; knit("jss_hyper3_real.Rnw")' && pdflatex jss_hyper3_real && open jss_hyper3_real.pdf
%

@@

@@

<<readsushi>>=
a <- as.matrix(read.table("sushi.txt",skip=22))
wanted <- sample(seq_len(nrow(a)), 5, replace=TRUE, prob=a[,1])
a <- a[wanted, -1]
@

<<tryH,cache=TRUE>>=

H1888 <- make_sushi_H(a, strength=1.888)
H1000 <- make_sushi_H(a, strength=1.000)
@

<<calclikesushi, cache=TRUE>>=
f <- function(strength){
   H <- make_sushi_H(a, strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=4,len=5)
L <- sapply(s,f)
@

@@
